---
title: | 
  Title here 
author: |
  *Author One* </br> Rutgers University </br> email@rutgers.edu
header-includes:
   - \usepackage{tipa}
output:
  drposter::drposter_poster:
    self_contained: false
    css: custom.css
    fill_page: false
---

```{r, load-packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(gt)
```




# {.col-2 .theme-minimalist}

## Intro

### Present study

- This is an itemized list
- It can contain as many items as you like

### Previous studies

References are cited as numbers. Here are a few examples. 
Previous studies found that certain things happen \cite{cho2007prosodically}. 
Another person found that another thing happened \cite{guion2003vowel}, but 
some people don't agree with the results \cite{amengual2012interlingual}.

- Itemized lists
- Can also be nested
  - Like this
  - and this
    - and this
    - and this

### Research Questions

1. We can also make numbered lists
2. Which can also be nested
  1. These are good for your hypotheses
  2. another item







## Method

### Materials

- Materials used
- Participants
- Stimuli
- Etc.
- item

### Procedure

- This is what we did
- This is how we did it
- So and so did it this way too
- Some examples here would be handy
- item

### Analysis

- The data were like this...
- This is how we analyzed it.
- So and so did this too
- This is the best way
- Here is an example...

```{r, formula, eval=FALSE}
dv ~ iv1 + iv2 + (1 + iv1 | id)
```


```{r, test-table, echo=FALSE}
tribble(
     ~' ',  ~'Lead', ~'Short-lag', ~'Long-lag',
'English',       '',      '/bdg/',     '/ptk/',
'Spanish',  '/bdg/',      '/ptk/',          ''
) %>% 
  gt()
```









# {.col-2 .theme-minimalist}

## Results

```{r}
cars %>% 
  gather(var, val) %>% 
  group_by(var) %>% 
  summarize(mean_value = mean(val), sd_value = sd(val)) %>% 
  gt
```

```{r, echo=FALSE}
ggplot(mtcars, aes(x = drat, y = mpg)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Conclusion

### Summary

- The analysis showed A
- The analysis showed B too.
- And don't forget about C, which was also important.

### Conclusion

- We learned X, Y, and Z.
- This research is in align with A and B
- But differs from what this other guy found
- Future research should do more things






## References

Take a look around the project example for a tour of useful column classes, etc.

## Ackowledgements

Somebody probably helped you. Thank them here. :)

